\bf\mftitle

### 2011-02-25 doc/jInfer/autoeditor/autoeditor.tex
Documentation: AutoEditor.

TODO prelozit
Ak je nejaka genericka trieda parametrizovana typom \code{T}, tak pri instanciovani tejto triedy je nutne tento typ zadat rovnaky, akym je instanciovany automat, pre ktory sa tato trieda vyraba. JUNG triedy su vacsinou parametrizovane typom pre stav a hranu. V takom pripade sa tieto triedy instanciuju typmi \code{State\textless T\textgreater} pre stav a \code{Step\textless T\textgreater} pre hranu. Refer to \cite{archdoc} for more information on these classes and see \ref{subsubsection:StatePickingComponent} and \ref{subsubsection:StatesPickingComponent} for source code examples.

@@

Purpose of this class is to be extended to create own GUI panel, which displays some automaton using a supplied instance of \code{Visualizer}. Method \code{getAutomatonDrawPanel()} is meant to be overridden to returns an instance of \code{JPanel}, in which the \code{Visualizer} is to be drawn.\\

@@

\subsubsection{StatesPickingComponent} \label{subsubsection:StatesPickingComponent}
Classes \code{StatePickingComponent} and \code{StatesPickingVisualizer} are similar to the classes described in the previous section. Purpose of these is to provide picking of multiple automaton states.\\

@@

\begin{figure}
\centering\includegraphics[scale=0.6]{screenshot}
\caption{Screenshot of \jmodule{AutoEditor} GUI} \label{figure_gui}
\end{figure}

As shown at figure \ref{figure_gui}, \jmodule{AutoEditor}'s panel is placed in a tab in the editor window. It consists of two buttons, horizontal line below them and and a panel to place an extension of \code{AbstractComponent} (see \ref{subsubsection:AbstractComponent}). Class representing this panel is named \code{AutoEditorTopComponent} and resides in \code{cz.cuni.mff.ksi.jinfer.autoeditor.gui.topcomponent} package.\\

>>>>

In case a generic class has a type parameter \code{T}, this has to be the same \code{T} that is used to parametrize jInfer automata. JUNG classes usually need a type parameter for a state and for an edge. These should be then \code{State\textless T\textgreater} (for a state) and \code{Step\textless T\textgreater} (for edge).

@@

Purpose of this class is to be extended to create own GUI panel, which displays some automaton using a supplied instance of \code{Visualizer}. Method \code{getAutomatonDrawPanel()} is meant to be overridden to return an instance of \code{JPanel}, in which the \code{Visualizer} is to be drawn.\\

@@

\subsubsection{StatesPickingComponent} \label{subsubsection:StatesPickingComponent}
\begin{figure}
\centering\includegraphics[scale=0.6]{screenshot}
\caption{Screenshot of \jmodule{AutoEditor} GUI} \label{figure_gui}
\end{figure}

Classes \code{StatePickingComponent} and \code{StatesPickingVisualizer} are similar to the classes described in the previous section. Purpose of these is to provide picking of multiple automaton states.\\

@@

As shown at figure \ref{figure_gui}, \jmodule{AutoEditor}'s panel is placed in a tab in the editor window. It consists of two buttons, horizontal line below them and a panel to place an extension of \code{AbstractComponent} (see \ref{subsubsection:AbstractComponent}). Class representing this panel is called \code{AutoEditorTopComponent} and resides in \code{cz.cuni.mff.ksi.jinfer.autoeditor.gui.topcomponent} package.\\
